\documentclass[a4paper]{article}

\usepackage[romanian]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{combelow}
\usepackage{newunicodechar}

\newunicodechar{Ș}{\cb{S}}
\newunicodechar{ș}{\cb{s}}
\newunicodechar{Ț}{\cb{T}}
\newunicodechar{ț}{\cb{t}}
\newunicodechar{Ă}{\cb{A}}
\newunicodechar{ă}{\cb{a}}
\newunicodechar{Â}{\cb{A}}
\newunicodechar{â}{\cb{a}}
\newunicodechar{Î}{\cb{I}}
\newunicodechar{î}{\cb{i}}

\title{Inside NAV}
\author{Barcan Virgil-Gheorghe}

\begin{document}
\maketitle

\begin{abstract}
Your abstract.
\end{abstract}

\section{Sistemul de operare Android}
\subsection{Despre Android}
Android este un sistem de operare dedicat dispozitivelor mobile, smartphone-uri, smartwatch-uri, precum și TV-urilor sau chiar dispozitive din interiorul automobilelor.

Sistemul de operare Android este bazat pe un kernel de Linux și a fost construit pentru a fi folosit în principal pe dispozitive touchscreen. Este cel mai folosit sistem de operare disponibil pe dispozitive mobile încă din 2013.


\subsection{Versiunile Android}

Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2014-09-03T09:54:16.211Z:
%
% Here's an example comment!
%
To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.

\subsection{How to add Tables}

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. 

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{How to write Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i$$
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.


\subsection{How to create Sections and Subsections}

Use section and subsections to organize your document. Simply use the section and subsection buttons in the toolbar to create them, and we'll handle all the formatting and numbering automatically.

\subsection{How to add Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}

We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above.

\end{document}